\chapter{Introduction}

\justifying
\section{Background}

     Artificial satellites are foundational components of modern society. Satellites have played a huge role in communication, navigation, scientific research, military surveillance and the study of the solar system and beyond. 
     
     Artificial satellites are launched into space using rockets and are placed in orbit around the Earth or other celestial bodies using thrusters. Once in orbit, they remain in space and continuously circle around the Earth, following a specific path called an orbit.
     
     There are two main types of orbits for artificial satellites: geostationary orbit and low Earth orbit. Geostationary orbit is a circular orbit located at an altitude of approximately 36,000 kilometres above the Earth's equator. Satellites in this orbit appear to be stationary relative to a fixed point on Earth, making them ideal for communication and navigation purposes. Low Earth orbit, on the other hand, is an orbit located at an altitude of up to approximately 2,000 kilometres above the Earth's surface. Satellites in this orbit circle the Earth more frequently and are used for scientific research, remote sensing, and military surveillance.
     
     Artificial satellites are powered by solar panels that convert sunlight into electricity, which is used to operate the satellite's systems and instruments. They are also equipped with communication antennas that enable them to transmit and receive signals from Earth or other satellites.
     
     The first artificial satellite, Sputnik, was launched in 1957. The launch of the first
meteorological satellite, TIROS-1, in 1960 was followed by the U.S. The first Earth-observing satellite for land-based applications was Landsat-1, which was launched in 1972. Since then many more Earth-observing satellites have been put into orbit.  Overall, artificial satellites have revolutionized our ability to communicate, navigate, observe, and study our planet and the universe beyond. They have become an essential part of modern life, and their applications are only expected to increase in the future.
\\

The whole process of designing, building, and launching a satellite-flown remote sensing system is a very lengthy and costly process. The main driving force behind the enormously costly development
of space technology has been the military, where cost is not usually a problem. With the relaxation on restrictions for ownership and operation of Earth-observing satellites it is now possible for anyone to build and launch satellites.
\\

For more than a decade, CubeSats, or small satellites, have paved the way to
low-Earth orbit for commercial companies, educational institutions, and non-profit
organizations. These small satellites offer opportunities to conduct scientific
investigations and technology demonstrations in space in such a way that is
cost-effective, timely and relatively easy to accomplish. Due to their small size, CubeSats can be launched on smaller rockets or piggybacked on larger missions, allowing for more frequent and flexible deployment opportunities. The small size of CubeSats allows for faster development and testing of new technologies, which can be later applied to larger satellites or space missions.\\


A CubeSat is a class of miniaturized satellite based around a form factor consisting
of 10 cm cubes. CubeSats have a mass of no more than 2 kg per unit, and often use
commercial off-the-shelf (COTS) components for their electronics and structure.
CubeSats are put into orbit by deployers on the International Space Station, or
launched as secondary payloads on a launch vehicle. As of August 2021, more than
1,600 CubeSats have been launched.
\\

CubeSat missions benefit Earth in varying ways. From Earth imaging satellites that
help meteorologists to predict storm strengths and direction, to satellites that focus
on technology demonstrations to help define what materials and processes yield the
most useful resources and function best in a microgravity environment, the variety
of science enabled by CubeSats results in diverse benefits and opportunities for
discovery.

\section{Objective}

%To design and implement a fully autonomous power generation, storage and distribution
%system for a CubeSat
The aim of this project is to determine requirements for a typical CubeSat Electrical Power System (EPS) and develop a working prototype of the EPS for a CubeSat.

\section{Literature Review}
\justifying
The EPS is a critical component of a CubeSat as it powers all the subsystems in the satellite. There are different EPS architectures of based on DC bus regulation and interface of PV panels [1].

 This project focuses on the design of an EPS with a regulated DC bus and MPPT tracking.
%
%[1] shows the comparison between different CubeSat EPS architectures, from which we have identified the architecture with maximum power point tracking and a regulated DC buses to be most suitable for our application.
\\

Based on the difference between centralized and distributed architecture was discussed in [2] and we have selected centralized architecture.
\\

As discussed in [3], solar panels operate at their most efficient points with a power point tracking algorithm, allowing the extraction of maximum power from the solar panels. Hence, peak power transfer is preferred to direct power transfer.
\\

Different battery technologies used in CubeSats were discussed in [4] and Li-ion cells were selected as the energy storage device due to their high energy density and higher number of charge discharge cycles compared to LiPo and NiMH batteries.
\\

From [5], the optimum ambient temperature for charging a Lithium ion battery is +5°C to +45°C and thus, charging is limited to this range of temperature.